---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lzstring

<!-- badges: start -->
[![R-CMD-check](https://github.com/parmsam/lzstring-r/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/parmsam/lzstring-r/actions/workflows/R-CMD-check.yaml)
[![Test coverage](https://github.com/parmsam/lzstring-r/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/parmsam/lzstring-r/actions/workflows/test-coverage.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/lzstring)](https://CRAN.R-project.org/package=lzstring)
[![Monthly metacran downloads](https://cranlogs.r-pkg.org/badges/lzstring)](https://cran.r-project.org/package=lzstring)
[![Total metacran downloads](https://cranlogs.r-pkg.org/badges/grand-total/lzstring)](https://cran.r-project.org/package=lzstring)

<!-- badges: end -->


The goal of lzstring-r is to provide an R wrapper for the [lzstring C++ library](https://github.com/andykras/lz-string-cpp). [lzstring](https://github.com/pieroxy/lz-string) is originally a JavaScript library that provides fast and efficient string compression and decompression using a [LZ-based algorithm](https://en.wikipedia.org/wiki/Lempel–Ziv–Welch). Credit goes to [Winston Chang](https://github.com/wch) for spotting this missing R package and guiding me over at the R Shinylive repo—check out his awesome contributions which this repo is based on [here](https://github.com/posit-dev/r-shinylive/issues/70) and [here](https://github.com/posit-dev/r-shinylive/pull/71). Also, shoutout to Andy Kras for his implementation in C++ of lzstring, which you can find right [here](https://github.com/andykras/lz-string-cpp), and [pieroxy](https://github.com/pieroxy), the original brain behind lzstring in JavaScript—peek at his work over [here](https://github.com/pieroxy/lz-string). 

## Installation

You can install the released version of lzstringr from [CRAN](https://CRAN.R-project.org/package=lzstring) with:

``` r
install.packages("lzstring")
```

You can install the development version of lzstringr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("parmsam/lzstring-r")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(lzstring)

# text data
message = "The quick brown fox jumps over the lazy dog!";

compressed = lzstring::compressToBase64(message)
compressed

decompressed = lzstring::decompressFromBase64(compressed)
cat(decompressed)
```

### JSON data

```{r}
# JSON data
json_data <- list(name = "John Doe", age = 30, email = "john.doe@example.com")
json_string <- jsonlite::toJSON(json_data)

compressed = lzstring::compressToBase64(json_string)
compressed

decompressed = lzstring::decompressFromBase64(compressed)
identical(json_string, decompressed)
cat(decompressed)
```

### R code

```{r}
r_code <- '
library(dplyr)

data <- data.frame(
  name = c("John", "Jane", "Jake"),
  age = c(28, 22, 32),
  salary = c(50000, 60000, 55000)
)

# Filter data for age greater than 25
filtered_data <- filter(data, age > 25)

# Add a new column with updated salary
data <- mutate(data, updated_salary = salary * 1.05)
'
compressed = lzstring::compressToBase64(r_code)
compressed
decompose = lzstring::decompressFromBase64(compressed)
cat(decompose)
```

### Compress Shinylive Hashes

```{r example1-shinylive}
code <- 'library(shiny)
ui <- fluidPage(
  "Hello, world!"
)
server <- function(input, output, session) {
}
shinyApp(ui, server)'
files <- list(
  name = jsonlite::unbox("app.R"),
  content = jsonlite::unbox(code)
)
files_json <- jsonlite::toJSON(list(files))
files_lz <- lzstring::compressToEncodedURIComponent(as.character(files_json))
cat(paste0("https://shinylive.io/r/app/#code=", files_lz))
```

### Decompress Shinylive Hashes
```{r example2-shinylive}
x <- lzstring::decompressFromEncodedURIComponent("NobwRAdghgtgpmAXGKAHVA6VBPMAaMAYwHsIAXOcpMAMwCdiYACAZwAsBLCbDOAD1R04LFkw4xUxOmTERUAVzJ4mQiABM4dZfI4AdCPp0YuCsgH0WAGw4a6ACl2RHyxwDlnTAAzKAjJ+9MAEyeAJT64RAAAqq2GBR8ZPoaNExkCXYhiPpMOSpwZPJ0EEw0jhAAVIFioiAmihgQGUzlQQC+jvpgrQC6QA")
y <- jsonlite::fromJSON(x)
cat(y$name)
cat(y$content)
```
