---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lzstring

<!-- badges: start -->
[![R-CMD-check](https://github.com/parmsam/lzstring-r/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/parmsam/lzstring-r/actions/workflows/R-CMD-check.yaml)
[![Test coverage](https://github.com/parmsam/lzstring-r/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/parmsam/lzstring-r/actions/workflows/test-coverage.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/lzstring)](https://CRAN.R-project.org/package=lzstring)
[![Monthly metacran downloads](https://cranlogs.r-pkg.org/badges/lzstring)](https://cran.r-project.org/package=lzstring)
[![Total metacran downloads](https://cranlogs.r-pkg.org/badges/grand-total/lzstring)](https://cran.r-project.org/package=lzstring)
<!-- badges: end -->

The goal of **lzstring-r** is to provide an R wrapper for the [lzstring C++ library](https://github.com/andykras/lz-string-cpp). [lzstring](https://github.com/pieroxy/lz-string) is originally a JavaScript library that provides fast and efficient string compression and decompression using a [LZ-based algorithm](https://en.wikipedia.org/wiki/Lempel–Ziv–Welch).

Credit goes to [Winston Chang](https://github.com/wch) for spotting this missing R package and guiding me over at the R Shinylive repo—check out his awesome contributions which this repo is based on [here](https://github.com/posit-dev/r-shinylive/issues/70) and [here](https://github.com/posit-dev/r-shinylive/pull/71). Also, shoutout to Andy Kras for his implementation in C++ of lzstring, which you can find right [here](https://github.com/andykras/lz-string-cpp), and [pieroxy](https://github.com/pieroxy), the original brain behind lzstring in JavaScript—peek at his work over [here](https://github.com/pieroxy/lz-string). 

---

## Installation

You can install the released version of lzstring from [CRAN](https://CRAN.R-project.org/package=lzstring) with:

```r
install.packages("lzstring")
```

Or the development version from [GitHub](https://github.com/parmsam/lzstring-r):

```r
# install.packages("devtools")
devtools::install_github("parmsam/lzstring-r")
```

---

## Usage

### Basic Example

```{r example}
library(lzstring)

# Text data
message <- "The quick brown fox jumps over the lazy dog!"
compressed <- lzstring::compressToBase64(message)
compressed

decompressed <- lzstring::decompressFromBase64(compressed)
cat(decompressed)
```

---

### Compressing and Decompressing JSON

```{r}
json_data <- list(name = "John Doe", age = 30, email = "john.doe@example.com")
json_string <- jsonlite::toJSON(json_data)

compressed <- lzstring::compressToBase64(json_string)
compressed

decompressed <- lzstring::decompressFromBase64(compressed)
identical(json_string, decompressed)
cat(decompressed)
```

---

### Round-Trip for Complex R Objects

> **Note:** Always serialize complex R objects (lists, data frames, etc.) to JSON before compressing. After decompression, deserialize back to R.

```{r}
obj <- list(a = 1, b = "text", c = list(x = 1:3))
json <- jsonlite::serializeJSON(obj)
lz <- lzstring::compressToBase64(json)
json2 <- lzstring::decompressFromBase64(lz)
obj2 <- jsonlite::unserializeJSON(json2)
identical(obj, obj2) # TRUE
```

---

### R Code Example

```{r}
r_code <- '
library(dplyr)

data <- data.frame(
  name = c("John", "Jane", "Jake"),
  age = c(28, 22, 32),
  salary = c(50000, 60000, 55000)
)

# Filter data for age greater than 25
filtered_data <- filter(data, age > 25)

# Add a new column with updated salary
data <- mutate(data, updated_salary = salary * 1.05)
'
compressed <- lzstring::compressToBase64(r_code)
compressed
decompose <- lzstring::decompressFromBase64(compressed)
cat(decompose)
```

---

### Compress Shinylive Hashes

```{r example1-shinylive}
code <- 'library(shiny)
ui <- fluidPage(
  "Hello, world!"
)
server <- function(input, output, session) {
}
shinyApp(ui, server)'
files <- list(
  name = jsonlite::unbox("app.R"),
  content = jsonlite::unbox(code)
)
files_json <- jsonlite::toJSON(list(files))
files_lz <- lzstring::compressToEncodedURIComponent(as.character(files_json))
cat(paste0("https://shinylive.io/r/app/#code=", files_lz))
```

### Decompress Shinylive Hashes

```{r example2-shinylive}
x <- lzstring::decompressFromEncodedURIComponent("NobwRAdghgtgpmAXGKAHVA6VBPMAaMAYwHsIAXOcpMAMwCdiYACAZwAsBLCbDOAD1R04LFkw4xUxOmTERUAVzJ4mQiABM4dZfI4AdCPp0YuCsgH0WAGw4a6ACl2RHyxwDlnTAAzKAjJ+9MAEyeAJT64RAAAqq2GBR8ZPoaNExkCXYhiPpMOSpwZPJ0EEw0jhAAVIFioiAmihgQGUzlQQC+jvpgrQC6QA")
y <- jsonlite::fromJSON(x)
cat(y$name)
cat(y$content)
```

---

## Encoding and Limitations

> **Important:**  
> - lzstring operates on strings. For non-string or binary data, encode as JSON or base64 first.  
> - Always ensure your input is UTF-8 encoded.  
> - If you compress an R object directly (without serialization), the result may not decompress as expected.

---

## Troubleshooting

- **Why do I get an empty string after decompressing?**  
  This may happen if the input was not properly encoded, or if the compressed string is corrupted.

- **Why does my decompressed JSON fail to parse?**  
  Ensure you serialize your R object to JSON (or use `serializeJSON`) before compressing.

- **Can I compress binary data?**  
  Encode it as base64 or hex first, then compress the resulting string.

---

## Use Cases

- Sharing Shiny app code via URL (see [Shinylive](https://shinylive.io/r/app/))
- Compact storage of large JSON blobs
- Embedding compressed data in web apps
- **Automatic Shinylive links in documentation:**  
  The [roxy.shinylive](https://github.com/insightsengineering/roxy.shinylive) package uses lzstring to provide a [roxygen2](https://roxygen2.r-lib.org/) extension that automatically takes the code from the `@examples` tag and creates a URL to the [shinylive.io](https://shinylive.io/r/app/) service. During documentation build, a new section is added to the function manual containing the link and an iframe to the application itself.

---

## References

- [lz-string JavaScript library (pieroxy)](https://github.com/pieroxy/lz-string)
- [lz-string C++ port (Andy Kras)](https://github.com/andykras/lz-string-cpp)
- [Shinylive for R](https://github.com/posit-dev/r-shinylive)
- [roxy.shinylive](https://github.com/insightsengineering/roxy.shinylive)

---
